Nearest Neighbour Methods for Length of Stay Prediction

### 2015-03-07 papers/paper.tex
Add graphs for correlation and information gain feature selectors
Add overall tables and move plots into a separate file

\begin{figure*}[htbp]
\begin{subfigure}{.48\textwidth}
\includegraphics[width=\textwidth]{results/tr-nofs-acc.eps}
\caption{}
\label{}
\end{subfigure}%
\begin{subfigure}{.55\textwidth}
\includegraphics[width=\textwidth]{results/tr-nofs-auc.eps}
\caption{}
\label{}
\end{subfigure}

\begin{subfigure}{.48\textwidth}
\includegraphics[width=\textwidth]{results/tr-dinh-acc.eps}
\caption{}
\label{}
\end{subfigure}%
\begin{subfigure}{.55\textwidth}
\includegraphics[width=\textwidth]{results/tr-dinh-auc.eps}
\caption{}
\label{}
\end{subfigure}

\begin{subfigure}{.48\textwidth}
\includegraphics[width=\textwidth]{results/tr-expert-acc.eps}
\caption{}
\label{}
\end{subfigure}%
\begin{subfigure}{.55\textwidth}
\includegraphics[width=\textwidth]{results/tr-expert-auc.eps}
\caption{}
\label{}
\end{subfigure}

\begin{subfigure}{.48\textwidth}
\includegraphics[width=\textwidth]{results/tr-wrapper-acc.eps}
\caption{}
\label{}
\end{subfigure}%
\begin{subfigure}{.55\textwidth}
\includegraphics[width=\textwidth]{results/tr-wrapper-auc.eps}
\caption{}
\label{}
\end{subfigure}
\caption[]{Comparison of accuracy and AUC between classifiers for each non-threshold feature selection method, grouped by whether or not discretisation was applied.}
\label{}
\end{figure*}

@@

@@

>>>>

@@

\input{results/overall-trauma-acc.tex}
\input{results/overall-trauma-auc.tex}

@@

\input{results/tr-nothreshold-plots.tex}
\input{results/tr-corr-ig-plots.tex}

### 2015-03-07 papers/results/tr-corr-ig-plots.tex
Add overall tables and move plots into a separate file

\begin{figure}[htbp]
\begin{subfigure}{.48\textwidth}
\includegraphics[width=\textwidth]{images/results/tr-nofs-acc.eps}
\caption{}
\label{}
\end{subfigure}%
\begin{subfigure}{.55\textwidth}
\includegraphics[width=\textwidth]{images/results/tr-nofs-auc.eps}
\caption{}
\label{}
\end{subfigure}

\begin{subfigure}{.48\textwidth}
\includegraphics[width=\textwidth]{images/results/tr-dinh-acc.eps}
\caption{}
\label{}
\end{subfigure}%
\begin{subfigure}{.55\textwidth}
\includegraphics[width=\textwidth]{images/results/tr-dinh-auc.eps}
\caption{}
\label{}
\end{subfigure}

\begin{subfigure}{.48\textwidth}
\includegraphics[width=\textwidth]{images/results/tr-expert-acc.eps}
\caption{}
\label{}
\end{subfigure}%
\begin{subfigure}{.55\textwidth}
\includegraphics[width=\textwidth]{images/results/tr-expert-auc.eps}
\caption{}
\label{}
\end{subfigure}

\begin{subfigure}{.48\textwidth}
\includegraphics[width=\textwidth]{images/results/tr-cfs-acc.eps}
\caption{}
\label{fig:tr-nothreshold-cfs-acc}
\end{subfigure}%
\begin{subfigure}{.55\textwidth}
\includegraphics[width=\textwidth]{images/results/tr-cfs-auc.eps}
\caption{}
\label{}
\end{subfigure}
\caption{Comparison of accuracy and AUC between classifiers for each non-threshold feature selection method, grouped by whether or not discretisation was applied.}
\label{fig:tr-nothreshold}
\end{figure}

\begin{figure}
\ContinuedFloat

\begin{subfigure}{.48\textwidth}
\includegraphics[width=\textwidth]{images/results/tr-wrapper-acc.eps}
\caption{}
\label{}
\end{subfigure}%
\begin{subfigure}{.55\textwidth}
\includegraphics[width=\textwidth]{images/results/tr-wrapper-auc.eps}
\caption{}
\label{}
\end{subfigure}
\caption[]{Comparison of accuracy and AUC between classifiers for each non-threshold feature selection method, grouped by whether or not discretisation was applied.}
\label{}
\end{figure}

\begin{figure}[htbp]
\begin{subfigure}{\textwidth}
\includegraphics[width=\textwidth]{images/results/tr-corr.eps}
\caption{}
\label{fig:tr-threshold-corr}
\end{subfigure}
\caption[]{Comparison of accuracy and AUC between classifiers for feature selectors that discard features based on a threshold. Solid lines correspond to a result without discretisation, and dashed lines correspond to a result with discretisation.}
\label{fig:tr-threshold}
\end{figure}

\begin{figure}[htbp]
\ContinuedFloat
\begin{subfigure}{\textwidth}
\includegraphics[width=\textwidth]{images/results/tr-ig.eps}
\caption{}
\label{fig:tr-threshold-ig}
\end{subfigure}

\begin{subfigure}{\textwidth}
\includegraphics[width=\textwidth]{images/results/tr-oner.eps}
\caption{}
\label{fig:tr-threshold-oner}
\end{subfigure}
\caption{Comparison of accuracy and AUC between classifiers for feature selectors that discard features based on a threshold. Solid lines correspond to a result without discretisation, and dashed lines correspond to a result with discretisation.}
\end{figure}

>>>>

\begin{figure}[htbp]
\begin{subfigure}{1.1\textwidth}
\includegraphics[width=\textwidth]{results/tr-corr.eps}
\caption{}
\label{fig:tr-threshold-corr}
\end{subfigure}

\begin{subfigure}{1.1\textwidth}
\includegraphics[width=\textwidth]{results/tr-ig.eps}
\caption{}
\label{fig:tr-threshold-ig}
\end{subfigure}
\caption[]{Comparison of accuracy and AUC between classifiers for feature selectors that discard features based on a threshold. Solid lines correspond to a result without discretisation, and dashed lines correspond to a result with discretisation.}
\label{fig:tr-threshold}
\end{figure}
